Local simple connectedness of boundaries of hyperbolic groups

### 2020-03-11 paper.tex
Deleted an orphaned lemma
Lemma: p^infty_m = p_n_m\composed p^\infty_n
Also made lots of other changes

\todo{Affine vs simplicial}
\todo{Write introduction}
\todo{Hyperbolicity conventions}
\todo{Proofread section 3}

@@

Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for $G$.
Let $\delta \geq 0$ be such that the Cayley graph of $G$ with respect to $S$ is 
$\delta$-hyperbolic. Let $\dist(\cdot, \cdot)$ be the natural metric on the
Cayley graph.

@@

\begin{lemma}
  \todo{Orphaned}
  For $\xi \in \boundary G$ and $n - m \geq D + \delta$ the points $p^n_m
  \composed p^\infty_n (\xi)$ and $p^\infty_m(\xi)$ lie in a common simplex of
  $K_n^D$.
\end{lemma}

\begin{proof}
  By definition, $p^\infty_m(\xi)$ is contained in the simplex spanned by the set
  $\set{g \in S_m \suchthat \xi \in V_m(g)}$ and $p^n_m\composed p^\infty_n(\xi)$ is
  contained in the simplex spanned by $\{p^n_m(g) \suchthat g \in S_n \text{
  and } \xi \in V_n(g)\}$.  We show that the union
  \begin{equation*}
    \set{g \in S_m \suchthat \xi \in V_m(g)} \union \{p^n_m(g) \suchthat g \in S_n \text{ and } \xi \in V_n(g)\}
  \end{equation*}
  of these sets spans a simplex in $K_n$; this simplex then contains
  $p^\infty_m(\xi)$ and $p^n_m\composed p^\infty_n(\xi)$.  It is sufficient to
  prove that if $\xi \in V_m(g_1) \intersection V_n(g_2)$ for $g_1 \in S_m$ and
  $g_2 \in S_n$ then $\dist(g_1, p^n_m(g_2)) \leq D$.

  For $i = 1$ or $2$ let $\gamma_i$ be a geodesic ray with $\gamma_i(0) = e$ and
  $\gamma_i(\infty) = \xi$ such that $\dist(g_1, \gamma_1(m)) \leq 2\delta
  + 1$ and $\dist(g_2, \gamma_2(n)) \leq 2\delta+1$.  As in
  \cref{lem:psimplicial}, $\dist(p^n_m(g_2), \gamma_2(m)) \leq
  2\delta$, since $n-m \geq 3\delta+1$.  Then $\dist(p^n_m(g_2), g_1) \leq
  2\delta + 2\delta + 2\delta+1 \leq D$.
\end{proof}

@@

\begin{lemma}\label{lem:affinehomotopic}
  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
  q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
  and $q_{i_0}\restricted{C}$ are related by an homotopy.
\end{lemma}

@@

  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
\end{proof}

>>>>

\todo{Affine vs simplicial}
\todo{Write introduction}
\todo{Proofread all}

@@

\subsection{Hyperbolic groups and the Rips complex}

Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for
$G$.  Let $\dist(\cdot, \cdot)$ be the natural metric on the Cayley graph of
$G$ with respect to $S$; on $G$ this metric agrees with the word metric.

Let $\delta \geq 0$ be such that the Cayley graph of $G$ with respect to $S$ is
$\delta$-hyperbolic, meaning that all geodesic triangles in the Cayley graph of
$G$ are $\delta$-thin. To ameliorate the growth of constants later on we in
fact assume that all \emph{ideal} triangles (with vertices in $G \union
\boundary G$) are $\delta$-hyperbolic; this can be guaranteed by multiplying
$\delta$ by $4$.

@@

@@

\begin{lemma}\label{lem:affinehomotopic}
  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
  q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
  and $q_{i_0}\restricted{C}$ are homotopic.
\end{lemma}

@@

  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are homotopic for $i \geq i_0$. 
\end{proof}
